Type Refinements for the Working Class

### 2015-11-12 paper.tex
remark on implicit definitions of judgments
remove (w \in W)
typos

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ and a worlds
category $\mathcal{W}$, we may deploy a general logical framework in which the
meaning of a judgment is an object of the presheaf category
$\Define{\mathbb{J}}{\Sets^\mathcal{W}}$ (that is, a judgment is identified
with the intensional set of its derivations).

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as the following product:
  \[
    \Define{[\Omega]}{
      \prod_{\MV{m}:v} \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]
  Let $\Discrete{[\Omega]}$ be the discrete category on $[\Omega]$. Then, for
  any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\Discrete{[\Omega]}}}$, we can
  define the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows:
  \[
    \textstyle
    \Define{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varinjlim_{\Discrete{[\Omega]}}\mathcal{J}
      }
    }\qquad
    (\Member{w}{\mathcal{W}})
  \]

@@

>>>>

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ and small worlds
category $\mathcal{W}$, we may deploy a generic logical framework in which the
meaning of a judgment is an object of the presheaf category
$\Define{\mathbb{J}}{\Sets^\mathcal{W}}$ (that is, a judgment is identified
with the intensional set of its derivations).

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as the following product:
  \[
    \Define{[\Omega]}{
      \prod_{\MV{m}:v} \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]
  Let $\Discrete{[\Omega]}$ be the discrete category on $[\Omega]$. Then, for
  any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\Discrete{[\Omega]}}}$, we can
  define the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows:
  \[
    \textstyle
    \Define{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varinjlim_{\Discrete{[\Omega]}}\mathcal{J}
      }
    }
  \]

@@

After this section, we will define a judgment either by rules, or by an
informal semantical explanation, in both cases leaving its intensional
character implicit. A judgment will said to be \emph{correct} or \emph{valid}
in case it is globally inhabited.
